%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jingnan(Jane)   Cao} % Your name
\address{(+1)951-756-6291 \\ jingnan.cao@email.ucr.edu  \\ 534 Palo Verde Common, Fremont, CA 94539} 
\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
%------------------------------------
{\bf University of California, Riverside} \hfill {09/2016 - 12/2017}\\ 
{\bf MS.} in {\bf Computer Engineering} - GPA: 3.64/4.00
\hfill { Riverside, CA}\\
\underline{Relevant Course}: HPC, GPU and Parallel Program, Info Retrieval \& Web Search, DB Management Systems, Design \& Analysis of Algorithms, Network Routing, Advanced Computer Networks, Computer Graphics\\
\\
 %------------------------------------
{\bf Beijing University of Posts and Telecommunications} \hfill {09/2011 - 07/2015}\\ 
{\bf BEng.} in {\bf Computer Science \& Technology} - Major GPA: 3.58/4.00
\hfill {Beijing, China}
 %------------------------------------
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{TECHNICAL SKILLS}
 %------------------------------------
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages &  Java, C/C++, Python, JSP, HTML, JS, PHP, SQL, MATLAB\\ 
Libraries/Frameworks &  Structs2, Spring, Hibernate, CUDA, OpenMPI, Lucene, Hadoop, OpenGL
\end{tabular}
 %------------------------------------
\end{rSection}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{WORK EXPERIENCES}
%------------------------------------
\begin{rSubsection}{Software Engineer – Intern    @    Yunnan Yajin Technologies Ltd. }{07/2013 - 08/2013} {} {} 
\item Developed application of Hospital Clinical Information System with back-end {\bf C++} and GUI {\bf Qt}. 
\item Assisted in the {\bf MySQL} databases maintenance.
\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{Research Engineer    @    Kunming University of Science and Technology}{ 01/2013 - 02/2013}{Applied Mathematics Lab, instructed by Prof. Yiping Lin } {}
 \item Developed a simulator to dynamically adjust experimental parameters by {\bf C}.
 \item Calculated data and generated figures by mainly {\bf MATLAB} and some auxiliary programs.
\end{rSubsection}
 %------------------------------------
\end{rSection}
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
 %------------------------------------
\begin{rSubsection}{R-tree Indexes Spatial Database}{05/2017 - 06/2017}{}{}
\item Developed a system to build {\bf R-tree} indexes on locations and trajectories datasets by {\bf Scala}.
\item Filtered data and implemented spatial queries of traffic by {\bf Simba} framework.
\item Used {\bf Hadoop} {\bf MapReduce} to calculate and sort query results. 
\end{rSubsection}
 %------------------------------------
\begin{rSubsection}{3D Render Pipeline \& Ray Tracer}{01/2017 - 02/2017}{}{} 
\item Implemented a 3D rendering pipeline by {\bf C++} under {\bf Linux}, including vertex and viewing transformations, rasterization, interpolation, clipping and using a z-buffer for hidden surface. Verified correctness by {\bf OpenGL}. 
\item Developed a ray tracer by {\bf C++} under {\bf Linux}, including ray generation, ray intersection, shading and reflection.
\end{rSubsection} 
 %------------------------------------
\begin{rSubsection}{Depixelizing Pixel Art}{02/2017 - 03/2017}{}{} 
\item Generated similarity network of pixel by {\bf Python}. Connected similar color pixels with a smooth edge by \emph{networkx}. 
\item Resolved the crossing edges by designed heuristics and reshaped pixel cells, then extracted spline curves. 
\item Rendered vector image output by \emph{svgwrite}.
\end{rSubsection} 
%------------------------------------------------
\end{rSection} 
%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{PUBLICATIONS} 
%------------------------------------------------
\begin{rSubsection}{Global Hopf Bifurcation on Two-Delays Leslie-Gower Predator-Prey System with a Prey Refuge}{} {} {} 
\item In Computational and Mathematical Methods in Medicine, Volume 2014 (2014), Article ID 619132 
\end{rSubsection}
%------------------------------------------------
\begin{rSubsection}{Chaos and Hopf Bifurcation Analysis of the Delayed Local Lengyel-Epstein System}{} {} {} 
\item In
Discrete Dynamics in Nature and Society, Volume 2014 (2014), Article ID 139375
\end{rSubsection}
%------------------------------------------------
\end{rSection}
%------------------------------------------------
\end{document}
